---
title: "Muppet (Molly)"
output:
  html_document:
    css: "style.css"
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scoll: false
---

\setlength\parindent{25pt}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)
```

```{r}
# build a function that creates spell dataframes
spell_creation <- function(cast, range, comp, duration, attack, effect) {
  castc <- c(cast)
  rangec <- c(range)
  compc <- c(comp)
  durationc <- c(duration)
  attackc <- c(attack)
  effectc <- c(effect)
  
  spell <- data.frame(castc, rangec, compc, durationc, attackc, effectc) %>% 
    rename("Casting Time" = castc, "Range/Area" = rangec, "Components" = compc,
           "Duration" = durationc, "Attack/Save" = attackc, "Damage/Effect" = effectc)
  return(spell)
}
```

# Character Sheet

```{r} 
# build the character sheet dataframe and display it
labels <- c("Stat", "Modifier")
STR <- c(14, "+2")
DEX <- c(17, "+3")
CON <- c(16, "+3")
INT <- c(7, "-2")
WIS <- c(8, "-1")
CHA <- c(10, "+0")

charsheet <- data.frame(labels, STR, DEX, CON, INT, WIS, CHA) %>% 
  rename(" " = labels)

kable(charsheet) %>% 
  kable_styling() %>% 
  column_spec(1, bold=T)

```


<hr class="new">

**Level**: 3

**Hit points**: 21

- Number of hit dice: 1 d10 per fighter level

**Proficiency bonus**: +2

**Saving throw proficiencies**: STR, CON

- Gnome Cunning: advantage against magical effects targeting: INT, WIS, CHA

**Armor class**: 15

**Perception check** is d20 + WIS modifier (WIS check); **initiative** is d20 + DEX modifier (DEX check).

<hr class="new">

## Skills
- Acrobatics [DEX]
- Perception [WIS]
- History [INT]: See Gnome Traits

### Languages
- Fluent in Common, Gnomish
- Can write rudimentary Dwarven script

### Weapon and tool proficiencies
- All armor, shields
- Simple weapons, martial weapons
- Tinker's tools

<details><summary>Tinker's tools: Click here to expand</summary>
You have proficiency with artisan’s tools (tinker’s tools). Using those tools, you can spend 1 hour and 10 gp worth of materials to construct a Tiny clockwork device (AC 5, 1 hp). The device ceases to function after 24 hours (unless you spend 1 hour repairing it to keep the device functioning), or when you use your action to dismantle it; at that time, you can reclaim the materials used to create it. You can have up to three such devices active at a time. When you create a device, choose one of the following options:

- **Clockwork Toy**: This toy is a clockwork animal, monster, or person, such as a frog, mouse, bird, dragon, or soldier. When placed on the ground, the toy moves 5 feet across the ground on each of your turns in a random direction. It makes noises as appropriate to the creature it represents.
- **Fire Starter**: The device produces a miniature flame, which you can use to light a candle, torch, or campfire. Using the device requires your action.
- **Music Box**: When opened, this music box plays a single song at a moderate volume. The box stops playing when it reaches the song’s end or when it is closed.
</details>

## Gnome Traits
- **Speed**: 25 feet base walking speed
- **Size**: 3'2.5" tall, 41 lbs; size Small
- **Darkvision**: Accustomed to life underground, you have superior vision in dark and dim conditions. You can see in dim light within 60 feet of you as if it were bright light, and in darkness as if it were dim light. You can’t discern color in darkness, only shades of gray.
- **Gnome Cunning**: You have advantage on all Intelligence, Wisdom, and Charisma saving throws against magic.


<hr class="new">

# Current Equipment

## Weapons/Armor

```{r}

studded_armor <- data.frame(name="Studded leather armor", damage="N/A", weight="13 lb.",
                     prop="12 + DEX modifier", type="Light armor")

rapier <- data.frame(name="Rapier", damage="1d8 piercing", weight="2 lb.", prop="Finesse",
                     type="Martial melee weapon")

scimitar <- data.frame(name="Scimitar", damage="1d6 slashing", weight="3 lb.", prop="Finesse, 
                       light", type="Martial melee weapon")

dagger <- data.frame(name="Dagger", damage="1d4 piercing", weight="1 lb.", 
              prop="Finesse, light, thrown (20/60)", type="Simple melee weapon")

magic_dagger <- data.frame(name="Magic dagger", damage='""', weight='""', prop='"" and +1 attack', 
                           type='""')

crossbow <- data.frame(name="Crossbow, light", damage="1d8 piercing", weight="5 lb.",
                 prop="Ammunition, range (80/320), loading, two-handed", type="Martial ranged weapon")

crossbow_bolts <- data.frame(name="Crossbow bolts", damage="N/A", weight="N/A", prop="39 bolts", 
                             type="Ammunition")

weaparmor <- rbind(studded_armor, rapier, scimitar, dagger, magic_dagger, crossbow, crossbow_bolts) %>% 
  rename(Name=name, Damage=damage, Weight=weight, Properties=prop, Type=type)

kable(weaparmor) %>% 
  kable_styling()
```

### Weapon Properties

<details><summary>Finesse</summary>
When making an attack with a finesse weapon, you use your choice of your Strength or Dexterity modifier for the attack and damage rolls. You must use the same modifier for both rolls.</details>

<details><summary>Light</summary>
A light weapon is small and easy to handle, making it ideal for use when fighting with two weapons.</details>

<details><summary>Thrown</summary>
If a weapon has the thrown property, you can throw the weapon to make a ranged attack. If the weapon is a melee weapon, you use the same ability modifier for that attack roll and damage roll that you would use for a melee attack with the weapon.</details>

<details><summary>Range</summary>
A weapon that can be used to make a ranged attack has a range shown in parentheses after the ammunition or thrown property. The range lists two numbers. The first is the weapon’s normal range in feet, and the second indicates the weapon’s maximum range. When attacking a target beyond normal range, you have disadvantage on the attack roll. You can’t attack a target beyond the weapon’s long range.</details>

<details><summary>Ammunition</summary>
You can use a weapon that has the ammunition property to make a ranged attack only if you have ammunition to fire from the weapon. Each time you attack with the weapon, you expend one piece of ammunition. Drawing the ammunition from a quiver, case, or other container is part of the attack. Loading a one-handed weapon requires a free hand. At the end of the battle, you can recover half your expended ammunition by taking a minute to search the battlefield. If you use a weapon that has the ammunition property to make a melee attack, you treat the weapon as an improvised weapon.</details>

<details><summary>Loading</summary>
Because of the time required to load this weapon, you can fire only one piece of ammunition from it when you use an action, bonus action, or reaction to fire it, regardless of the number of attacks you can normally make.</details>

<details><summary>Two-Handed</summary>
This weapon requires two hands to use. This property is relevant only when you attack with the weapon, not when you simply hold it.</details>

<details><summary>Improvised Weapons</summary>
If a character uses a ranged weapon to make a melee attack, or throws a melee weapon that does not have the thrown property, it deals 1d4 damage. An improvised thrown weapon has a normal range of 20 feet and a long range of 60 feet.</details>

<hr class="new">

## Belongings

### Travel: Explorer's Pack

- backpack
- bedroll
- mess kit
- tinderbox
- 10 torches
- 10 days of rations
- waterskin
- 50 feet of hempen rope

### Personal (excluding equipped)

- 68 gold
- Leather armor (original, unequipped)
- Treasure map with an **X** labeled "something here should stay buried" in Dwarven
- Handy spice pouch
    - Magically gives you a pinch of however much spice you need for a meal
    - Works 10x/day, recharges 1d6+4 charges toward max each day at dawn)
- Hat of vermin
    - Use an action to speak a command that summons either a bat, frog, or rat
    - The animal disappears after 1 hour or after its HP reaches 0
    - The hat has 3 charges that refresh daily at dawn
- Boots of false tracks
    - Leaves tracks like another humanoid of my size


<hr class="new">


# Fighting

### Fighting Style: Two-Weapon Fighting

When you engage in two-weapon fighting, you can add your ability modifier to the damage of the second attack.

### Second Wind

You have a limited well of stamina that you can draw on to protect yourself from harm. On your turn, you can use a bonus action to regain hit points equal to 1d10 + your fighter level. Once you use this feature, you must finish a short or long rest before you can use it again.

### Action Surge

You can push yourself beyond your normal limits for a moment. On your turn, you can take one additional action. Once you use this feature, you must finish a short or long rest before you can use it again. Starting at 17th level, you can use it twice before a rest, but only once on the same turn.

## Martial Archetype: Battle Master

You know three maneuvers of your choice; you can use only one maneuver per attack.

**Superiority Dice**. You have four superiority dice, which are d8s. A superiority die is expended when you use it. You regain all of your expended superiority dice when you finish a short or long rest. You gain another superiority die at 7th level and one more at 15th level.

**Saving Throws**. Some of your maneuvers require your target to make a saving throw to resist the maneuver's effects. The saving throw DC is calculated as follows:

- Maneuver save DC = 8 + your proficiency bonus + your Strength or Dexterity modifier (your choice)

### Parry

When another creature damages you with a melee attack, you can use your reaction and expend one superiority die to reduce the damage by the number you roll on your superiority die + your Dexterity modifier.

### Trip Attack

When you hit a creature with a weapon attack, you can expend one superiority die to attempt to knock the target down. You add the superiority die to the attack's damage roll, and if the target is Large or smaller, it must make a Strength saving throw. On a failed save, you knock the target prone.

### Quick Toss

As a bonus action, you can expend one superiority die and make a ranged attack with a weapon that has the thrown property. You can draw the weapon as part of making this attack. If you hit, add the superiority die to the weapon's damage roll.



<hr class="new">

# Background

**Race**: [Rock Gnome](https://www.dndbeyond.com/races/gnome)

**Class**: [Fighter](https://www.dndbeyond.com/classes/fighter)

Muppet is a pirate. She has always been a pirate. She is very good at climbing ropes. She likes to do trick shots with her dagger, especially when the ship is moving. She has been chastised for this. She will do it again, probably.

Or: Muppet, previously Molly, is a naval deserter. Her parents are bigwigs in the navy and she was shoved into a naval apprenticeship, which she ran away from, putting her skills to good use as a pirate. She now goes by Muppet, and does not tell people her old name.

She is very quick on her feet and fairly cheerful, but has a vicious streak when fighting. She will divert you away from any mention of her past. She built a group of good friends on the pirate crew; she likes hanging out with people and doing tricks. She loves food. Food available on the ground is so much better than ship food. Grilled corn! Meat on sticks! Delightful.

## Campaign Notes

<details><summary>
1/27/24: Muppet Stabs A Man (In The Eye)
</summary>

She insists on scouting Saltmarsh before her crew loots it because she wants to see if there's anything in town she has to avoid/lead her crewmates away from (i.e. potential connections to the navy or anyone that would recognize her). Her crew is used to her paranoia and lets her do her thing. She sticks with Wendell and Eleza because she would rather have people around, and some people is better than none.

She is coerced into doing the gig for the Duke, but she doesn't intend to follow through; she has no incentive to help the law enforcement crack down on pirates, given that she herself wants to loot the town with her pirate crew (or warn the crew off from town). Her pirate philosophy is if they don't bother her, she doesn't bother them, so she really didn't want to fight the other pirates, especially since she thought they'd be outnumbered. Once she saw Dad Grundle she tried to de-escalate, and failed miserably. But since he kidnapped her, and she doesn't actually mean to return the stuff to town, she may as well steal his stuff...
</details>

<details><summary>
2/3/24: Muppet Loses A Finger (It Gets Glued On Again But Wrong)
</summary>
Muppet talks with Dad (Bjorn) Grundle, who seems resigned to being turned in to the Duke. Muppet returns his wedding ring (the simple copper ring) by sliding it onto his hook-hand, but keeps everything else. She wanders up to the crow's nest while everyone else is debating what to do with the pirate crew, then comes back down and plays stabby stabby with her dagger and her hand on the deck. Interested, Basil (half-elf, pirate crew, snacking on a fish and picking fish out of her teeth with her sword) comes over and starts stabbing too. She cuts off Muppet's finger by accident. Muppet bravely keeps it together while Wendell fails to reattach her finger correctly; her left ring finger has been reattached at a 45 degree angle. Woops.

Back on shore, everyone else talks to the Duke and discusses returning his stuff to get Eleza's ring back. Muppet wanders off and finds Bobby Grundle, buying him corn. The Duke is upset that all his money is gone, and sends Alucard to fetch Muppet. Muppet leaves her bag full of gold with Bobby and returns with Alucard; she returns the Duke's seal, but not his money. Unfortunately, Bobby comes running up with her bag, and the Duke simply grabs the bag and takes back his money. Muppet had squirreled away two fistfuls of gold coins in her pocket, though, so the Duke doesn't get it all back. Suck it.

The party goes to The Wicker Goat, a dwarven bar near the mines, and meets Darcy, a young dwarf that's killer at poker, and Tholdir, her father-figure and union agitator. Muppet gets drunk on a tall pink drink. (We realize the mysterious dwarven device was a _Geiger counter_. Fuck.) The dwarves take everyone to meet Gaia, a mysterious genius tall for a dwarf drop-dead gorgeous nuclear physicist, who realizes Wendell is a physicist from the university and thinks he's here to steal her science. The party goes into the mines for a tour, fight off a cave fisher (big bug), and are almost drowned by Gaia, who is "cooling" the mines by flooding it with seawater. They escape through a crack in the ceiling...

</details>

<details><summary>
2/18/24: Muppet vs. Magic Goldfish Swarm
</summary>
The crew crawls out of the tunnel system and emerges onto a cliffside graveyard overlooking the sea, where they meet Crag, a half-ogre groundskeeper and Saltmarsh historian. Muppet befriends Crag and learns that he has the whole town's blueprints memorized, and that they can all go look at the blueprints at the Saltmarsh Historical Society.

The next day, the crew goes to the Historical Society, where they meet Anora - the person that had greeted Muppet, Eleza, and Wendell at the ferry landing. Anora is pleased to show them around and talks about architecture with Eleza while Muppet hangs out with Crag, who is delicately brushing artifacts.

Eleza talks Anora into giving them a tour of the barracks-turned-prison, and the crew goes to the prison, where they meet [??? C-name], a human guard. Muppet decides to pretend to be an overeager child (minor retcon of previous Anora meeting? Lol. Anora can think she is a precocious child come to meet her dad in town). Upon Muppet's avid curiosity, the crew + Anora + 2 guards goes down into the actual jail-level, where we hear Peck and Bjorn Grundle's voices in one of the cells.

After a couple unsuccessful attempts at breaking them out, Muppet causes a distraction by asking a guard for non-saltless-Saltine snacks, and the guard gives her goldfish, which she drops on the floor and then promptly starts wailing crocodile tears over it. Everyone is panicked about Muppet's crying, which means Alucard has a chance to steal the guard's keys and unlocks the doors (or maybe Elpida did?). The human guard upstairs shuts the door between basement and first-floor. races to the door and beats on it crying "LET ME OUT!" in as scared-little-girl voice as she can manage, and the door opens again and the prisoners escape. The crew manages to get away while seemingly innocent.

Muppet still has not heard from her pirate crew... But she is not thinking about that.

</details>


<details><summary>
2/25/24: All Hail Frogphet
</summary>
The crew miraculously faces no suspicion for the prison break, but learns from the Duke that a weapons smuggler escaped, one that they fear is selling weapons to the community of lizard people that live across the marsh. The crew is tasked with going to talk to the lizard people, guided by a bigoted human guard named Clayton.

While still in town, they go shopping, and Muppet switches out several of her weapons and also buys a hat of vermin and a pair of boots of false tracks. Wendell kisses a frog. Wendell x Frog Benediction 200k slowburn.

They go through the marsh guided by Clayton that day. They run into a community of potentially hostile frog people, but Muppet uses her hat of vermin to summon three frogs and present them to the frog people, convincing them that she is a frogphet and to let her (and her company) pass without incident. They also face a quicksand pit, which they cross by various hempen rope maneuvers (Muppet almost dies!).

Once at the lizard people's community, Muppet does her best to befriend the lizard kids, but they're kind of sensitive, and there's also a serious language barrier. Meanwhile, Eleza and Wendell try to negotiate with the adults - Eleza uses her Draconic language skills. They finish the session talking to a lizard minister in the temple dedicated to the lizard people's god.
</details>