---
title: "Muppet (Molly)"
output:
  html_document:
    css: "style.css"
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scoll: false
---

\setlength\parindent{25pt}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)
```

```{r}
# build a function that creates spell dataframes
spell_creation <- function(cast, range, comp, duration, attack, effect) {
  castc <- c(cast)
  rangec <- c(range)
  compc <- c(comp)
  durationc <- c(duration)
  attackc <- c(attack)
  effectc <- c(effect)
  
  spell <- data.frame(castc, rangec, compc, durationc, attackc, effectc) %>% 
    rename("Casting Time" = castc, "Range/Area" = rangec, "Components" = compc,
           "Duration" = durationc, "Attack/Save" = attackc, "Damage/Effect" = effectc)
  return(spell)
}
```

# Character Sheet

```{r} 
# build the character sheet dataframe and display it
labels <- c("Stat", "Modifier")
STR <- c(14, "+2")
DEX <- c(17, "+3")
CON <- c(16, "+3")
INT <- c(7, "-2")
WIS <- c(8, "-1")
CHA <- c(10, "+0")

charsheet <- data.frame(labels, STR, DEX, CON, INT, WIS, CHA) %>% 
  rename(" " = labels)

kable(charsheet) %>% 
  kable_styling() %>% 
  column_spec(1, bold=T)

```


<hr class="new">

**Level**: 2

**Hit points**: 17

- Number of hit dice: 1 d10 per fighter level

**Proficiency bonus**: +2

**Saving throw proficiencies**: STR, CON

- Gnome Cunning: advantage against magical effects targeting: INT, WIS, CHA

**Armor class**: 14

A **perception check** is d20 + WIS modifier (WIS check); roll for **initiative** is d20 + DEX modifier (DEX check).

<hr class="new">

## Skills
- Acrobatics [DEX]
- Perception [WIS]
- History [INT]: See Gnome Traits

### Languages
- Fluent in Common, Gnomish
- Can write rudimentary Dwarven script

### Weapon and tool proficiencies
- All armor, shields
- Simple weapons, martial weapons
- Tinker's tools

<details><summary>Tinker's tools: Click here to expand</summary>
You have proficiency with artisan’s tools (tinker’s tools). Using those tools, you can spend 1 hour and 10 gp worth of materials to construct a Tiny clockwork device (AC 5, 1 hp). The device ceases to function after 24 hours (unless you spend 1 hour repairing it to keep the device functioning), or when you use your action to dismantle it; at that time, you can reclaim the materials used to create it. You can have up to three such devices active at a time. When you create a device, choose one of the following options:

- **Clockwork Toy**: This toy is a clockwork animal, monster, or person, such as a frog, mouse, bird, dragon, or soldier. When placed on the ground, the toy moves 5 feet across the ground on each of your turns in a random direction. It makes noises as appropriate to the creature it represents.
- **Fire Starter**: The device produces a miniature flame, which you can use to light a candle, torch, or campfire. Using the device requires your action.
- **Music Box**: When opened, this music box plays a single song at a moderate volume. The box stops playing when it reaches the song’s end or when it is closed.
</details>

## Gnome Traits
- **Speed**: 25 feet base walking speed
- **Size**: 3'2.5" tall, 41 lbs; size Small
- **Darkvision**: Accustomed to life underground, you have superior vision in dark and dim conditions. You can see in dim light within 60 feet of you as if it were bright light, and in darkness as if it were dim light. You can’t discern color in darkness, only shades of gray.
- **Gnome Cunning**: You have advantage on all Intelligence, Wisdom, and Charisma saving throws against magic.


<hr class="new">

# Current Equipment

## Weapons/Armor

```{r}
Item <- c("Studded leather armor", "Dagger", "Crossbow, hand", "Rapier", "Crossbow bolts")
Damage <- c("N/A", "1d4 piercing", "1d6 piercing", "1d8 piercing", "N/A")
Weight <- c("10 lb.", "1 lb.", "3 lb.", "2 lb.", "N/A")
Properties <- c("12 + DEX modifier", "Finesse, light, thrown (20/60)", "Ammunition, range (30/120), light, loading", "Finesse", "39 bolts")
Type <- c("Light armor", "Simple melee weapon", "Martial ranged weapon", "Martial melee weapon", "Ammunition")

Weaparmor <- data.frame(Item, Damage, Weight, Properties, Type)

kable(Weaparmor) %>% 
  kable_styling()
```

### Weapon Properties

<details><summary>Finesse</summary>
When making an attack with a finesse weapon, you use your choice of your Strength or Dexterity modifier for the attack and damage rolls. You must use the same modifier for both rolls.</details>

<details><summary>Light</summary>
A light weapon is small and easy to handle, making it ideal for use when fighting with two weapons.</details>

<details><summary>Thrown</summary>
If a weapon has the thrown property, you can throw the weapon to make a ranged attack. If the weapon is a melee weapon, you use the same ability modifier for that attack roll and damage roll that you would use for a melee attack with the weapon.</details>

<details><summary>Range</summary>
A weapon that can be used to make a ranged attack has a range shown in parentheses after the ammunition or thrown property. The range lists two numbers. The first is the weapon’s normal range in feet, and the second indicates the weapon’s maximum range. When attacking a target beyond normal range, you have disadvantage on the attack roll. You can’t attack a target beyond the weapon’s long range.</details>

<details><summary>Ammunition</summary>
You can use a weapon that has the ammunition property to make a ranged attack only if you have ammunition to fire from the weapon. Each time you attack with the weapon, you expend one piece of ammunition. Drawing the ammunition from a quiver, case, or other container is part of the attack. Loading a one-handed weapon requires a free hand. At the end of the battle, you can recover half your expended ammunition by taking a minute to search the battlefield. If you use a weapon that has the ammunition property to make a melee attack, you treat the weapon as an improvised weapon.</details>

<details><summary>Loading</summary>
Because of the time required to load this weapon, you can fire only one piece of ammunition from it when you use an action, bonus action, or reaction to fire it, regardless of the number of attacks you can normally make.</details>

<details><summary>Improvised Weapons</summary>
If a character uses a ranged weapon to make a melee attack, or throws a melee weapon that does not have the thrown property, it deals 1d4 damage. An improvised thrown weapon has a normal range of 20 feet and a long range of 60 feet.</details>

<hr class="new">

## Belongings

### Travel: Explorer's Pack

- backpack
- bedroll
- mess kit
- tinderbox
- 10 torches
- 10 days of rations
- waterskin
- 50 feet of hempen rope

### Personal

- 9 gold, 9 silver, 6 copper (original)
- Leather armor (original, unequipped)

### Stolen items from Dad Grundle

- silver and copper coins (uncounted how many)
- Duke's official seal (idk what that is)
- Simple copper ring with signet (put it on)
- Treasure map with an **X**
- Strange object: short handled hammer with weather vane, pendulum
- 160 gold
- Studded armor (replaced leather armor, equipped)


<hr class="new">


# Fighting

### Fighting Style: Two-Weapon Fighting

When you engage in two-weapon fighting, you can add your ability modifier to the damage of the second attack.

### Second Wind

You have a limited well of stamina that you can draw on to protect yourself from harm. On your turn, you can use a bonus action to regain hit points equal to 1d10 + your fighter level. Once you use this feature, you must finish a short or long rest before you can use it again.

### Action Surge

Starting at 2nd level, you can push yourself beyond your normal limits for a moment. On your turn, you can take one additional action.

Once you use this feature, you must finish a short or long rest before you can use it again. Starting at 17th level, you can use it twice before a rest, but only once on the same turn.

<hr class="new">

# Background

**Race**: [Rock Gnome](https://www.dndbeyond.com/races/gnome)

**Class**: [Fighter](https://www.dndbeyond.com/classes/fighter)

Muppet is a pirate. She has always been a pirate. She is very good at climbing ropes. She likes to do trick shots with her dagger, especially when the ship is moving. She has been chastised for this. She will do it again, probably.

Or: Muppet, previously Molly, is a naval deserter. Her parents are bigwigs in the navy and she was shoved into a naval apprenticeship, which she ran away from, putting her skills to good use as a pirate. She now goes by Muppet, and does not tell people her old name.

She is very quick on her feet and fairly cheerful, but has a vicious streak when fighting. She will divert you away from any mention of her past. She built a group of good friends on the pirate crew; she likes hanging out with people and doing tricks. She loves food. Food available on the ground is so much better than ship food. Grilled corn! Meat on sticks! Delightful.

<details><summary>
1/27/24: Muppet Stabs A Man (In The Eye)
</summary>

She insists on scouting Saltmarsh before her crew loots it because she wants to see if there's anything in town she has to avoid/lead her crewmates away from (i.e. potential connections to the navy or anyone that would recognize her). Her crew is used to her paranoia and lets her do her thing. She sticks with Wendell and Eleza because she would rather have people around, and some people is better than none.

She is coerced into doing the gig for the Duke, but she doesn't intend to follow through; she has no incentive to help the law enforcement crack down on pirates, given that she herself wants to loot the town with her pirate crew (or warn the crew off from town). Her pirate philosophy is if they don't bother her, she doesn't bother them, so she really didn't want to fight the other pirates, especially since she thought they'd be outnumbered. Once she saw Dad Grundle she tried to de-escalate, and failed miserably. But since he kidnapped her, and she doesn't actually mean to return the stuff to town, she may as well steal his stuff...

</details>

